\documentclass{memoir}
\usepackage{notestemplate}

% \begin{figure}[ht]
%     \centering
%     \incfig{riemmans-theorem}
%     \caption{Riemmans theorem}
%     \label{fig:riemmans-theorem}
% \end{figure}

\begin{document}

\section{Finite Fields}
\label{sec:finite_fields}
\begin{thm}
	Let \(F\) be a finite field. \(\left| F \right| = p^{k}\), \(p\) prime. Conversely, for every \(p^{k}\) there exists exactly one \(F\) such that \(\left| F \right| = p^{k}\)
\end{thm}
\begin{proof}
We will show that the \( \textrm{dim} = k\); namely that there exists a basis \(b_1,\ldots,b_k\) that generates all elements in \(F\) uniquely by 
\begin{align*}
	a = \lambda_1 b_1 + \ldots + \lambda_k b_k
\end{align*}
where \(\lambda_1,\ldots,\lambda_k \in \Z_p\), which by our other theorem is a subfield. This is isomorphic to \(\Z_p[x] / (g)\) which is \(F\). Observe that \( \textrm{deg}g = k\)These are the residues mod \(g\), or
\begin{align*}
	a_0 + a_1x + \ldots + a_{k-1}x^{k-1}
\end{align*}
Each \(a_i\) can be chosen \(p\) ways, so then \(\left| F \right| = p^{k}\), as desired.
\end{proof}
\begin{thm}
	For any element \(a \in F\) a finite field,
	\begin{align*}
		a + \ldots + a = 0
	\end{align*}
	where \(a\) is added exactly \(p\) times.
\end{thm}
\begin{proof}
For all \(a\) there exists an \(n\) such that
\begin{align*}
	a+\ldots+a = 0
\end{align*}
when \(a\) is added \(n\) times, because eventually the sequence \(a, a+a, a+a+a, \ldots\) must repeat, and then you'll have your \(n\). There are infinite solutions, but finitely many elements in \(F\). This implies that
\begin{align*}
	a + \ldots + a = a + \ldots + a
\end{align*}
where on the LHS, \(a\) is added \(i\) times, and on the RHS added \(j\) times.\\
Assume that \(i < j\). Observe that
\begin{align*}
	a + \ldots + a = 0
\end{align*}
for \(j-i\) additions. Now assume that \(a \neq 0\). Then multiply both sides by \(b\) implies
\begin{align*}
	\forall b, b + \ldots + b = 0
\end{align*}
because we can factor. Thus the assumption holds. Now we want to find the smallest \(n>0\). Assume for the sake of contradiction that \(n = kl\), both greater than \(1\) (not prime). Then we can separate the sum into blocks of \(k\) and blocks of \(l\). Then
\begin{align*}
	\underbrace{a+\ldots+a}_k + \underbrace{\ldots}_{l} + \underbrace{a+\ldots+a}_k = 0
\end{align*}
By assumption  \(a+\ldots+a\) is non-zero, so it is some \(b \in F\). But then \(\underbrace{b+\ldots+b}_l = 0\), which is a contradiction. So it has to be prime, as desired.
\end{proof}
\begin{thm}
	Let \(F\) be a finite field. Then
	\begin{align*}
		F = \left\{ 0,1,\alpha,\alpha^2,\ldots,\alpha ^{\left| F \right| -2}\right\} 
	\end{align*}
	and \(\alpha ^{\left| F \right| -1} = 1\)
\end{thm}
\begin{thm}[Finite Field Extensions]
	For all finite fields \(F\),there exists an \(H\leq F\) such that \(H \cong \Z_p\) for some \(p\). Furthermore, \(F\) is a vector space over \(\Z^{p}\).
\end{thm}
\(F\) is then a field extension of \(H\).
Consider
\begin{align*}
	H = \left\{ 0,1,1+1,\ldots,\underbrace{1+\ldots+1}_{p-1} \right\} 
\end{align*}
Observe that adding and multiplying elements works like traditional addition and subtraction; namely that
\begin{align*}
(t\cdot 1)+(s\cdot 1) = (s+t) \pmod p \cdot 1
\end{align*}
for \(0\leq t\leq p-1\) and
\begin{align*}
	(\underbrace{1+\ldots+1}_t)\cdot (\underbrace{1+\ldots+1}_s) = ( ts) \pmod p \cdot 1
\end{align*}
and so the isomorphism to \(\Z_p\) holds, as all the elements can then be written by multiplication of \(0\leq t\leq p-1\) and \(1\).
\begin{thm}
	For any finite field \(F\), \(F \cong \Z_{p[x]} / (g)\) where \(g\) is a polynomial over \(\Z_p\), \( \textrm{deg }g = k\), \(g\) irreducible over \(\Z_p\)
\end{thm}
\end{document}
