\documentclass{memoir}
\usepackage{notestemplate}

%\logo{~/School-Work/Auxiliary-Files/resources/png/logo.png}
%\institute{Rice University}
%\faculty{Faculty of Whatever Sciences}
%\department{Department of Mathematics}
%\title{Class Notes}
%\subtitle{Based on MATH xxx}
%\author{\textit{Author}\\Gabriel \textsc{Gress}}
%\supervisor{Linus \textsc{Torvalds}}
%\context{Well, I was bored...}
%\date{\today}

\begin{document}

% \maketitle

% Notes taken on 05-10-21

\section{Techniques in Characteristic p > 0}
\label{sec:techniques_in_characteristic_p_0}

\begin{prop}
	Let \(F\) be a field of characteristic \(p>0\). Then for all \(a,b \in F\), we get that
	\begin{align*}
		(a+b)^{p} = a^{p} + b^{p}\\
		(ab)^{p} = a^{p}b^{p}
	\end{align*}
\end{prop}
This is the "Freshman's Dream".

\begin{defn}[Frobenius Endomorphism]
	For a field \(F\) of characteristic \(p>0\), the function
	\begin{align*}
		\varphi :F\to F\\
		a\mapsto a^{p}
	\end{align*}
	is the \textbf{Frobenius endomorphism} of \(F\).
\end{defn}
\begin{cor}
	The Frobenius endomorphism of \(F\) is an injective field homomorphism. When \(F\) is finite, it is also surjective.
\end{cor}

Now we will go back to some propositions about finite fields using these ideas.
\begin{prop}
	Every irreducible polynomial over a finite field \(F\) is separable. Moreover, \(f(x) \in F[x]\) is separable if and only if it is the product of distinct irreducible polynomials in \(F[x]\).
\end{prop}
This follows by contradiction. One can express the irreducible polynomial as a polynomial of the form \(g(x^{p})\), but this polynomial can be shown to be reducible, and so cannot occur.

\begin{defn}[Perfect]
	A field \(K\) of characteristic \(p>0\) is called \textbf{perfect} if every element of \(K\) is a \(p\)-th power in \(K\)-- that is, \(K = K^{p}\).
\end{defn}
By convention any field of characteristic zero is also called perfect.\\

We have just shown that every irreducible polynomial over a perfect field is separable, and hence finite extensions of perfect fields are separable.

\begin{hw}
	Prove that there exists a non-perfect infinite field \(F\), i.e. find \(f(x) \in F[x]\) so that \(f\) is irreducible and not separable.
\end{hw}

These concepts can be used to prove that the \(n\)-th cyclotomic polynomial \(\Phi_n(x) \in \Z[x]\) is irreducible.

\end{document}
