\documentclass[num=0,duedate=01-27-21,course=Abstract\ Algebra\ II,proflastname=Walton]{hwtemplate}

%%% Options for hwtemplate.cls:
%
%% Required:
%
% num - Assignment number
% course - Name or course ID
% proflastname - Last name of professor
% duedate - date that homework is due, in mm-dd-yy
%
%% Optional:
%
% type - type of document (default: Homework)
% studentid - student id used for emails etc. (default: gjg3)
% name - your full name (default: Gabriel Gress)
% emaildomain - domain of email (default: rice.edu)
%
%%%

\begin{document}

\lstset{language=Matlab,%
	%basicstyle=\color{red},
	breaklines=true,%
	morekeywords={matlab2tikz},
	keywordstyle=\color{blue},%
	morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
	identifierstyle=\color{black},%
	stringstyle=\color{mylilas},
	commentstyle=\color{mygreen},%
	showstringspaces=false,%without this there will be a symbol in the places where there is a space
	numbers=left,%
	numberstyle={\tiny \color{black}},% size of the numbers
	numbersep=9pt, % this defines how far the numbers are from the text
	emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
	%emph=[2]{word1,word2}, emphstyle=[2]{style},
}

% \lstinputlisting{foo.m}

\maketitle
\pagebreak

\section{Practice Problems}
\label{sec:practice_problems}

\problem[1]
\begin{claim}
	What is your first name?
\end{claim}

\begin{proof}
Gabriel
\end{proof}

\problem[2]
\begin{claim}
	What name would you like to be referred?
\end{claim}
\begin{proof}
Gabe
\end{proof}

\problem[3]
\begin{claim}
	What are your preferred pronouns?
\end{claim}
\begin{proof}
	He/him
\end{proof}

\problem[4]
\begin{claim}
	What is your major?
\end{claim}
\begin{proof}
	I am pursuing a B.S. in MATH
\end{proof}

\separator

\section{Advanced Problems}
\label{sec:advanced_problems}

\problem[5]
\begin{claim}
	Why are you interested in MATH 357?
\end{claim}
\begin{proof}
From a pragmatic standpoint:\\
My interests primarily lie in analysis and PDEs, the latter of which often utilizes aspects of abstract algebra such as Lie groups or semigroups. I also believe in having a strong foundation.\\

From a personal standpoint:\\
Abstract algebra is super fun and I love writing the proofs for it! I also find the history of Galois theory super fascinating, and so I look forward to learning the kinds of things that Galois jumpstarted.
\end{proof}

\problem[6]
\begin{claim}
	What are your goals for the course and for the semester?
\end{claim}
\begin{proof}
For the course:\\
My goals are to build a foundation solid enough that I can comfortably utilize the core concepts (modules, finite fields) when they pop up in other fields of mathematics. I also want to succeed (i.e. get an A) and generally have fun interacting with you and my peers.\\

For the semester:\\
I am faced with a particularly heavy semester (this course + algebraic topology + differential geometry + topics in PDEs), and so I will be working crazy hard to stay on top of my work. I also have mental health concerns I am working very hard this semester to address, so overall my main goals are to maintain motivation and personal health.
\end{proof}

\problem[7]
\begin{claim}
	Please share a fun fact about yourself.
\end{claim}
\begin{proof}
I am super passionate about film and board games. Do you have a favorite movie or a movie you would recommend?
\end{proof}

\end{document}
